Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-06 sources/bmc_template_submission/bmc_article.tex
answering soem more questions

%% Biological plausibility of example??

>>>>

%% Biological plausibility of example??
The updated holly tree is based on a single marker, so we expected for it to be
not as well resolved as trees using multiple markers. Nevertheless, all samples
corresponding to the ingroup cluster together in a monophyletic group. We also
note that most samples belonging to the same species also cluster together forming
monophyletic groups. Notable exceptions are Ilex theeizans, which also appears as
non-monophyletic in the original Gottlieb et al. 2005 tree. A visual comparison
of the Yao et al. 2020 tree and the original Gottlieb et al. 2005 tree suggests
that the relationships within the genus Ilex are still being determined, and that
increased taxon sampling is helping with it.
